---
title: "Homework 1"
author: "Canan Güç 21080423"
---

```{r global_options, include=FALSE}
# Do not delete or modify this chunk.
# We will cover chunk options later.
# This is required for Question 7
library(knitr)
opts_chunk$set(fig.align="center", fig.height=4, fig.width=5.5)
```

**Question 1** With Markdown write a sentence that has one word in bold.

**hello word**


**Question 2** With Markdown write a sentence that has one word in italic.

*hello world*

**Question 3** With Markdown write a sentence that has one word in italic bold.

***hello world***

**Question 4** With Markdown write an unordered list with three items.

* Elma
* Domates
* Un

**Question 5** With Markdown write an ordered list with three items.

1. Elma
2. Domates
3. Un

**Question 6** With Markdown give a link to your favorite webpage.

[linked phrase](https://www.trendyol.com/butik/liste/1/kadin)


**Question 7** With Markdown add a cat picture.

![yelling cat]https://www.ctvnews.ca/polopoly_fs/1.4692721.1574189694!/httpImage/image.jpg_gen/derivatives/landscape_620/image.jpg


**Question 8** With Rmarkdown insert a code chunk and give an example of a simple mathematical calculation in it.

```
2+2=4
```


**Question 9** With $LaTeX$ write your favorite equation in block form.

$7-2=5$

**Question 10** In a code chunk calculate 3 + 4.
```{r}
```


```{r}
plot(7)
```

